---
title: "Package Tutorial"
author: "Basanta Khakurel"
date: "`r Sys.Date()`"
output: html_document
---

# This is the tutorial file for my R Package. 

You might have already seen the introduction section of the website. It has a hint on what the data looks like. 
So let's get started by downloading the simulated data set and the empirical data set. These data contain the summary statistics of the simulated and empirical data generated by a Bayesian phylogenetic software called `RevBayes`. 

```{r}
library(tidyverse)
library(janitor)
library(PPS.Analysis)
```


The data to this tutorial can be found here. Download this file and put it in a folder called 'data'. 
[Simulated Data](https://raw.githubusercontent.com/basanta33/PPS.Analysis/main/data/simulated_data_pps_data.csv) 
[Empirical Data](https://raw.githubusercontent.com/basanta33/PPS.Analysis/main/data/empirical_data_pps_data.csv)


### Function 1: Renaming the Columns

If we open the csv files containing the data I generated, first we notice that the names of columns are really well-written and it somwhow makes it uneasy to work with codes, so the first thing we'll be doing is renaming the columns of the csv files. 

My first function reads the data and changes the names of columns to a more code-friendly one.  

```{r}
#loading in the simulated data set and cleaning the column names
simdata <- rename_col("../data/simulated_data_pps_data.csv")
#loading in the empirical data set and cleaning the column names
empdata <- rename_col("../data/empirical_data_pps_data.csv")
```

In addition to cleaning the names for the data read in the environment, it also saves the column-changed data to a csv file. 

***

### Function 2: Removing Unnecessary Columns

As we take a look at the cleaned data file, we see that it contains a lot of columns, most of which having all the values 0. The data was generated using morpholgical character sets so we would not have certain summary statistics like GC content (which is one of the valuable summary statistics for molecular sequence). So, the second function I have will get rid of the columns that has all values 0. 

```{r}
```

***

### Function 3: Linear Model between two columns of the data set

***

### Function 4: Effect Size Calculation 

***

### Function 5: Plotting 

***
***








